### 2015-12-14 paper/4-performance.tex
Spelling and esthetical changes

\begin{figure}
    \includegraphics[width=\columnwidth,height=6.5cm]{fig/phold_remotes.eps}
    \caption{Phold benchmark results for parallel simulation using 6 cores, with varying fraction of remote events.}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth,height=6.5cm]{fig/phold_priority.eps}
    \caption{Phold benchmark results for parallel simulation using 6 cores, with varying amount of high-priority events.}
    \label{fig:phold_priority}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\columnwidth,height=6.5cm]{fig/phold_remotes.eps}
    \caption{Phold benchmark results for parallel simulation using six cores, with varying fraction of remote events.}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth,height=6.5cm]{fig/phold_priority.eps}
    \caption{Phold benchmark results for parallel simulation using six cores, with varying amount of high-priority events.}
    \label{fig:phold_priority}
\end{figure}
